---
title: "Ploteando No Detectados"
subtitle: "Presentation by Ing. A.Otiniano"
author: "Ing. A.Otiniano"
institute: "UNI"
output: 
  beamer_presentation:
    theme: "CambridgeUS"
    #colortheme: "dolphin"
    fonttheme: "professionalfonts"
    toc: true # Table of contents
    slide_level: 2  # Enable subsections (optional)
    keep_tex: false # keeps the .tex generated (also images)
    latex_engine: xelatex # Latex engine
    incremental: true
    includes:
      in_header: mystyle.tex
date: "`r Sys.Date()`"
header-includes: # format latex (you can add from latex)
- \logo{\includegraphics[width= 2cm]{figura/logo.png}}
  \AtBeginDocument{\setbeamertemplate{navigation symbols}[horizontal]}  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Objetivos 

* Entender el concepto de  **Survival Analysis**.

* Conocer los diferentes **Límites de Reporte**.

* Diferenciar los **Límites de Detección y Cuantificación**.

# R Markdown

## Data

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

\begincols
  \begincol{.30\textwidth}

This slide has two columns.

  \endcol
\begincol{.70\textwidth}

```{r}
#No error here i can run any r code
plot(cars)
```

  \endcol
\endcols


# Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

# Slide with Plot

```{r pressure, out.width='80%', fig.align='center', fig.cap='Ploteo'}
plot(pressure)
```

